Toronto Paramedic Services

### 2024-09-25 paper/paper.qmd
tried importing data, but didn't work - need to try again later
figured out the problem of reading in data for map!

>>>>

## Mapping EMS Demand

```{r}
#| echo: false 
#| message: false
#| label: fig-map
#| fig-cap: EMS Demand Across Toronto Forward Sortation Areas (Based on data from 2022)

library(maps)
library(sf)

data <- read_csv(here::here("data/analysis_data/analysis_data_FOR_MAP.csv"))

# Reading in the shapefile
#toronto_forward_sortation_areas <- st_read("~/Toronto_Paramedic_Services/data/TorontoForwardSortationAreas")
